---
date: "Last compiled on `r format(Sys.time(), '%d %B, %Y')`"
author: "Kristy Robledo"
title: "Statistical Report for the EXAMPLE trial"
output: 
  officedown::rdocx_document:
    reference_docx: template.docx 
    page_margins:
      bottom: 1
      top: 1
      right: 1
      left: 1
      header: 0.5
      footer: 0.5
      gutter: 0

knit: (function(inputFile, encoding) {rmarkdown::render(inputFile, encoding = encoding, output_file = paste0("EXAMPLE-statistical-report-", Sys.Date(),".docx")) })
---

```{r setup, include=FALSE}
## setup chunk

knitr::opts_chunk$set(echo = FALSE, fig.cap = TRUE)

##read in packages for reporting
library(officedown)
library(officer)
library(flextable)
library(sessioninfo)

## read in packages for analyses
library(tidyverse)
library(gtsummary)
library(ggsurvfit)

####  formatting helpers  ###################################################################


fp <- fp_par(                                         ##underline
  text.align = "center", 
  padding.bottom = 20, padding.top = 120, 
  border.bottom = fp_border())

ft <- fp_text(shading.color='#EFEFEF', bold = TRUE)   ##format text

ft_title <- fp_text(font.size=16,                     ##format a title not in TC
                    font.family = "Calibri",
                    shading.color = "transparent", 
                    bold = TRUE)       


whitespace <- fp_par(                                 ##create whitespace
  text.align = "center", 
  padding = 30, 
)

set_flextable_defaults(font.family = "Calibri", 
                       font.size = 9, 
                       padding=2, 
                       table.layout = "autofit"
                      )

theme_gtsummary_journal(journal = "jama")

####  load data  ###############################################################


#install.packages("ipcwswitch")
library(ipcwswitch)
data("SHIdat")

#glimpse(SHIdat)

#### derive datasets ##########################################################
SHIdat %>%
  mutate(days = case_when(progStatus==1 ~ progDate-as.Date("1jan2012", "%d%b%Y"), 
                          progStatus==0~ as.Date("1jan2016", "%d%b%Y")-as.Date("1jan2012", "%d%b%Y")) ) ->survdf

#write.csv(survdf, file="SHIdat-surv.csv")
```


\newpage


`r ftext("Table of contents", ft_title)` 

<!---BLOCK_TOC--->

## List of figures

<!---BLOCK_TOC{seq_id: 'fig'}--->

## List of tables

<!---BLOCK_TOC{seq_id: 'tab'}--->


\newpage

# Baseline

Here is the table one for the report. 

```{r,tab.id="table1",  tab.cap="Table one by treatment"}

SHIdat %>%
  select(bras.f, sex.f, agerand, pathway.f, tt_Lnum) %>%
  tbl_summary(by=bras.f, 
              statistic = list(agerand ~ "{mean} ({sd})", 
                               tt_Lnum ~ "{median} ({min}-{max})"), 
              label = list(agerand ~ "Age in years")) %>%
  add_overall() %>%
  as_flex_table()
```


# Progression free survival

Please see Table \@ref(tab:table1) for baseline. 

<!---BLOCK_LANDSCAPE_START--->
```{r, fig.cap="PFS by treatment", fig.dim=c(10,6)}

br<-seq(0, 365*5, by=365)

survdf %>%
  survfit2(Surv(days, progStatus) ~ bras.f, .) %>%
  ggsurvfit() +
  labs(x= "Years from randomisation", 
       y="PFS") +
  add_risktable() +
  scale_ggsurvfit(x_scales = list(breaks = br, 
                                  labels = round(br/365, 2)))

```


<!---BLOCK_LANDSCAPE_STOP--->


```{r, tab.id="pfscox", tab.cap="Cox model for PFS"}
coxph(Surv(days, progStatus) ~bras.f, data=survdf) %>%
  tbl_regression(exponentiate = TRUE) %>%
  as_flex_table()
```



```{r, tab.id="tblsurv", tab.cap="Survival times table"}

survdf %>%
survfit2(Surv(days, progStatus) ~ bras.f, .) %>% 
  tbl_survfit(times=c(365,365*2),
              label_header = "**{time} days**") %>%
  as_flex_table()
```





this is how to create a list

- one
- two 
- three

`r whitespace`

order list 

1. one
1. two 
1. three


# Reproducibility receipt

Analyses and summaries produced in this report were carried out using the R statistical environment, version `r paste(version$major, version$minor, sep=".")`. The report itself was produced using an Rmarkdown workflow, located here: `r knitr::current_input(dir = TRUE)``. The following table lists the non-base R packages used in analyzing and building this report.  


```{r, tab.cap = "R packages used in analyses and reporting"}
sessioninfo::package_info() %>%
  unclass() %>%
  as_tibble() %>%
  filter(attached==TRUE) %>%
  select(package, ondiskversion, date) %>%
  rename(version=ondiskversion) %>%
  flextable()
  
```

